### 2025-05-13 Title/approval.tex
changes of panel

This thesis entitled \textbf{\enquote{SleepGCN-Transformer: A Hybrid Graph
Convolutional and Transformer Network for Sleep
Stage Classification}} by \textbf{Tanmay Rathod} is recommended for the degree of \textbf{M.Tech} in \textbf{Artificial Intelligence}.
\vspace{0.8cm}

\hspace{9cm}  
\begin{flushright}   
    \makebox[1.8in]{\hrulefill}\\
    Guide : Dr Santosh Satapathy, \\
    Assistant Professor \\
    Dept. of ICT \\

\end{flushright}
\vspace{0.5cm}

\hspace{9cm}  
\begin{flushright}   
    \makebox[1.8in]{\hrulefill}\\
    Dr Nitin Singh Rajput, \\
    Assistant Professor \\
    Dept. of ICT
\end{flushright}
\vspace{0.5cm}

% \hspace{9cm}\\
\begin{flushright}
    \makebox[1.8in]{\hrulefill}\\
    Dr. Paawan Sharma,\\
    Head Of Department \\ 
    Dept. of ICT
\end{flushright}

>>>>

This thesis entitled \textbf{\enquote{SleepGCN-Transformer: A Hybrid Graph Convolutional and Transformer Network for Sleep Stage Classification}} by \textbf{Tanmay Rathod} is recommended for the degree of \textbf{M.Tech} in \textbf{Artificial Intelligence}.

\vspace{1cm}

\begin{table}[h!]
	\centering
	\begin{tabular}{@{}m{0.45\textwidth}<{\centering} m{0.45\textwidth}<{\centering}@{}}
		\textbf{Guide} & \textbf{Panel Members} \\[4em]
		\rule{0.4\textwidth}{0.4pt} & \rule{0.4\textwidth}{0.4pt} \\[1em]
		Dr. Santosh Satapathy, & Member 1, \\[1em]
		Assistant Professor, & Designation, \\[1em]
		Dept. of ICT & Dept. of ICT \\[2em]
		\textbf{Head of Department} & \\ [4em]
		\rule{0.4\textwidth}{0.4pt} & \rule{0.4\textwidth}{0.4pt} \\[1em]
		Dr. Paawan Sharma & Member 2, \\[1em]
		HoD, Dept. of ICT, & Designation,\\[1em]
		School of Technology & Designation\\[1em]
	\end{tabular}
\end{table}
